Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-02 main.tex
Robotic implementation (for now copy pasted from HRI paper)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Robotic Embodiement}
\begin{figure}[ht]
\centering

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Robotic Implementation}

In order to develop a teachable agent that is appropriate for engaging a child
in the learning by teaching paradigm, we have established capabilities for the
robot to engage in handwriting and interactive turn-taking.

The {\sc nao} V4 humanoid robot, which has been purposely designed by Aldebaran
Robotics to look approachable~\cite{Gouaillier2008}, is used for this work. It
is a commercially affordable biped robot, 58cm tall, with 25 degrees of freedom,
two cameras, speech capabilities and the ability to autonomously execute a range
of tasks.

Precise control over what the robot is writing is necessary in the proposed
application of a handwriting. Because of the limited fine motor skills possible
with such an affordable robot, in addition to the absence of force feedback and
other technical necessities, we have configured the {\sc nao} to use simulated
handwriting with a synchronised tablet to achieve this level of control.

The development of the necessary components for embedding the handwriting
learning algorithm presented in Section \ref{sec:learningAlgorithm} in the
humanoid agent are presented in the sections which follow.

\subsubsection{Robot Trajectory Following Movements}

Using simulated handwriting provides an opportunity for the robot's writing to
appear smoother than would be achievable with a writing instrument. However, the
robot's motions must still sufficiently match the displayed trajectory in order
capture the engagement of the child participant in the action. Aldebaran's NaoQi
API is used for the inverse kinematics of the trajectory following. The Robot
Operating System (ROS)\footnote{The ROS stack for {\sc nao} is available at:
\url{http://wiki.ros.org/nao_robot}.} is used for integration of the {\sc nao}
with external reference frames, such as the tablet's location, using the $tf$
transformation library \cite{Foote2013}.

When using simulated handwriting, it is no longer necessary that the robot
engages in the typical style of handwriting of using a writing instrument at a
desk.  Having the robot point at a vertical writing surface to cause the
trajectory to appear (as in Figure \ref{fig:naoWriting}) has several advantages:

\begin{itemize}

    \item The working space of the robot increases, both in the technical sense
        and the interaction sense: someone can, in theory, show the tablet to
        the robot from across the room and have it still respond, without
        needing the tablet to be within arm's reach.

    \item Concerns about whether or not the child would start mimicking the
        robot's incorrect writing form (\eg pen grip) are mitigated.

    \item Perhaps most significantly, the accuracy of the matching of the
        robot's motion with the trajectory displayed on the tablet is not as
        critical. This is because a pen tip would be expected to touch the
        tablet exactly at the trajectory point, while a fingertip may not.

\end{itemize}

\begin{figure}[thpb]
     \begin{center}
            \includegraphics[width=0.7\linewidth]{naoWriting2.png}
    \end{center}
    \caption{A demonstration of the robot simulating the writing of a word with
    its finger. The motion of the robot is synchronised with the display of the
    tablet, communicating over ROS.}%

   \label{fig:naoWriting}
\end{figure}

We have therefore designed the system in such a way that the robot is simulating
handwriting by pointing at the tablet\footnote{Teachers interviewed for their
feedback on the system advised that children are asked to draw letters in
the air in a similar manner as part of their handwriting education. The
behaviour is hence not unfamiliar to children.}. As interacting with a
tablet with one's finger is not uncommon, this may aid the acceptance of the
writing style by users.

Because motion planning is performed with respect to the hand of the robot,
rather than its fingertip, one or two of the orientation degrees of freedom of
the hand are fixed to keep the finger approximately perpendicular to the writing
surface, depending on the desired accuracy. The remaining free orientation(s),
coupled with the whole-body motion control available, allow for a sufficient
working space for writing on the entire tablet.

\begin{figure}[ht]
\centering
